---
title: "p8105_hw1_yc4016"
output: github_document
date: "2022-09-23"
author: "Yishan Chen"
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

##### Load `penguins` dataset.

```{r setup_dataset}
data("penguins", package = "palmerpenguins")
```

* The name of variables are `r names(penguins)`. 
  * Some important value: 
    * The mean of flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digit = 2)` mm.
    * The median of flipper length is `r round(median(pull(penguins, flipper_length_mm), na.rm = TRUE), digit = 2)` mm.
    * The mean of bill length is `r round(mean(pull(penguins, bill_length_mm), na.rm = TRUE), digit = 2)` mm.
    * The median of bill lengthis `r round(median(pull(penguins, bill_length_mm), na.rm = TRUE), digit = 2)` mm.
* The size of the dataset are `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean of flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digit = 2)` mm.

##### Make the scatter plot. 

```{r scatter_plot, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 5, width = 5)
```



# Problem 2

##### Create dataframe.

```{r setup_dataframe, warning = FALSE}
hw1p2_df = tibble(
  vec_norm = rnorm(10),
  vec_logical = vec_norm > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "g", "i", "j"),
  vec_factor = factor(c("level1", "level2", "level3", "level1", "level2", "level1", "level1", "level2", "level3", "level1"))
)
hw1p2_df
```


##### Take the mean of each variable.

```{r mean_of_variables}
mean(pull(hw1p2_df, vec_norm))
mean(pull(hw1p2_df, vec_logical))
mean(pull(hw1p2_df, vec_char))
mean(pull(hw1p2_df, vec_factor))
```

* We can take the mean of numeric variable and logical variable.
* We cannot take the mean of a character variable and factor variable, which has results NA. 


```{r convertion, include = FALSE}
as.numeric(pull(hw1p2_df, vec_logical))
as.numeric(pull(hw1p2_df, vec_char))
as.numeric(pull(hw1p2_df, vec_factor))
```

* After converting logical, character, and factor variables into numeric variable, we can take the mean of logical and factor variables. However, we still cannot take the mean of a character variable. 

* The logical variables are stored as a distinct data type that TRUE is stored as 1 and FALSE is stored as 0. Factor variables are stored as integers. So after converting to the numeric, we can take the mean of logical and factor variables. However, character variable are stored as character, so we could not take the mean of it. Yes this helps explain what happened when you try to take the mean. 


